Discon Adult Analysis

### 2018-09-08 analysis/01_adult.Rmd
add adult experiment with all trials 6-0-0, add sound recordings for Pig, add analysis files for kids' pilot results and adults results

---
title: "Discon analysis"
output: html_document
---

@@

#Pilot 1 data
```{r data preprocessing}
# Data pre-processing

@@

data <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = ifelse(distribution == "2:0", "c(2, 1, 0)", distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)", "c(3, 0, 0)", "c(1, 1, 1)", "c(2, 1, 0)")))

 # data <- raw_data %>%
 #  mutate(correct_target3 = ifelse(correct_target1 == 0 & correct_target2 == 0, 1, 0)) %>%
 #  mutate(distribution = as.character(distribution),
 #         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")),
 #         pick = ifelse(pickPos == "item_l", item_l, ifelse(pickPos == "item_r", item_r, ifelse(pickPos=="item_m", item_m, NA))),
 #         correct_item = ifelse(pick == correctItem, 1, 0),
 #         pickTest = substr(pick, 4, length(pick)),
 #         correct_target1 = ifelse(pickTest == target1, 1, 0),
 #         correct_target2 = ifelse(pickTest == target2, 1, 0),
 #         correct_target3 = ifelse(pickTest == target3, 1, 0))

# write.csv(data, file="../data/pilot.data.csv")

# data <- read_csv(file="../data/pilot.data.csv")
```

```{r sanity checks}
data %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item))

drop <- data %>%
  filter(phase == 'training') %>%
  group_by(workerid) %>%
  summarise(correct = mean(correct_item)) %>%
  filter(correct < 0.83) %>%
  pull(workerid)

data <- data %>%
  filter(!workerid %in% drop)

```

# Some preliminary tests
```{r}
data_test <- data %>% 
  filter (phase == "test", distribution == "c(4, 2, 0)") %>%
  summarise (lastInput = mean(same_lastInput),
             n = length(distribution))
#23/38 trials

data_test <- data %>%
  filter(phase == "test", distribution == "c(6, 0, 0)") %>%
  summarise (correct1 = mean(correct_target1))

data_test <- data %>%
  filter(phase == "test", distribution == "c(2, 2, 2)") %>%
  summarise (lastInput = mean(same_lastInput),
             n = length(distribution))
# 23/38

```

# Salience of each category
```{r}
plot1 <- data %>%
  filter(phase == "test", distribution == "c(6, 0, 0)") %>%
  group_by(distribution, target1) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3))

plot1 <- data %>%
  filter(phase == "test", distribution == "c(6, 0, 0)", target1 == "vehicles")

# clothes: 2
# fruits: 5
# furniture: 10
# instruments: 4
# mammals: 8
# vehicles: 9

plot1 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid, target1) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid, -target1) %>%
  group_by(distribution, item, target1) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot1,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+
  facet_grid(target1~distribution) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")
```
# Do proportion of choices match the frequency in the distribution

```{r proportion of choices}
plot1 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid) %>%
  group_by(distribution, item) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot1,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+
  facet_grid(~distribution, 
             labeller = as_labeller(c(`c(5, 1, 0)` = "Distribution\n(5-1-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")
```
# How does the last item seen affect the object chosen in the anaphora case? 
```{r last item}
plot2 <- data %>%
  filter(phase == "test", distribution != "c(6, 0, 0)") %>%
  mutate(trackLast = ifelse(lastInputCat == target1, "yes", "no")) %>%
  group_by (distribution, workerid) %>%
  summarise (lastInput = mean(same_lastInput),
             n = n()) %>% 
  multi_boot_standard(col = "lastInput")

ggplot(plot2,
       aes(x = distribution, y = mean, fill = distribution)) +
  geom_bar(stat='identity', width = 0.3) +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few()
```

# Are there 2 strategies in determining what "another one" means?
```{r}
plot3 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid) %>%
  group_by(distribution, item)

plot3a <- plot3 %>%
  multi_boot_standard(col = "prop_correct")

ggplot() +
  geom_jitter(data = plot3, aes(x = item, y = prop_correct, col = distribution, alpha = .2), width = .3,height = .025)+
  geom_pointrange(data = plot3a, aes(x = item, y = mean, col = distribution, ymin = ci_lower, ymax = ci_upper),size = .8)+
  facet_grid(~distribution)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Item Chosen", y="Proportion Chosen")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
 # theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))

#No - if 2 strategies: there should be fewer dots in the middle
```
# Does where (5,1,0) occurs determine the strategy of chosing the last item?
```{r}
plot3 <- data %>%
  filter(phase == 'test', distribution == "c(5, 1, 0)") %>%
  mutate(distType = ifelse(trial < 4, "early", "late")) %>%
  group_by(distribution, workerid, distType) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid, -distType) %>%
  group_by(distribution, item, distType)

plot3a <- plot3 %>%
  multi_boot_standard(col = "prop_correct")

ggplot() +
  geom_jitter(data = plot3, aes(x = item, y = prop_correct, col = distribution, alpha = .2), width = .3,height = .025)+
  geom_pointrange(data = plot3a, aes(x = item, y = mean, col = distribution, ymin = ci_lower, ymax = ci_upper),size = .8)+
  facet_grid(~distType)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Item Chosen", y="Proportion Chosen")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
 # theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

# Does the graded distribution come through in cases where the last input does not affect the object choice?
```{r}
plot3 <- data %>%
  filter(phase == "test", distribution == "c(4, 2, 0)", same_lastInput == 0) %>%
  group_by(distribution, workerid) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid) %>%
  group_by(distribution, item) %>%
  multi_boot_standard(col = "prop_correct")

ggplot(plot3,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+
  facet_grid(~distribution, 
             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")
```

# Does the framing influence the match between choice and distribution

```{r plot 2}
plot2 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid, trialType) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid, -trialType) %>%
  arrange(workerid)

 # group_by(distribution, trialType, item) %>%
 # multi_boot_standard(col = "prop_correct")

ggplot() + 
  geom_jitter(data = plot2, 
              aes(x = item, y=prop_correct, fill=item, col=trialType),
              height = 0.1,
              width = 0.1) +
  facet_grid(trialType~distribution) +
  theme(legend.position="none")

plot2 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid, trialType) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid, -trialType) %>%
  group_by(distribution, trialType, item) %>% 
  multi_boot_standard(col = "prop_correct")

ggplot(plot2,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+
  facet_grid(trialType~distribution, 
             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")

```

# Comparing the last input with the picked object by distribution

```{r}
a <- data %>%
  filter(slide == 6) %>%
  select(workerid, pick)

b <- data %>%
  filter(slide == "choice") %>%
  select(workerid, distribution, pickCat, correct_target1)

b$pickSlide6 = a$pick

b <- b %>%
  filter(distribution != "c(6, 0, 0)", correct_target1 == 1) %>%
  arrange(distribution) %>%
  group_by(distribution) %>%
  summarise(n = length(distribution))

# 30/59 trials picking the same category as the last input slide.
# 24/33 for 4, 2, 0
# 7/26 for 2, 2, 2
```

# Are participants choosing the middle item more? 
```{r middle item}
plot3 <- data %>%
  filter(phase == 'test') %>%
  mutate(pick_l = ifelse(pickPos == "item_l", 1, 0), 
         pick_m = ifelse(pickPos == "item_m", 1, 0),
         pick_r = ifelse(pickPos == "item_r", 1, 0)) %>%
  group_by(distribution, workerid) %>%
  summarise(choose_l = mean(pick_l),
            choose_m = mean(pick_m),
            choose_r = mean(pick_r)) %>%
  gather(item, prop_choose, -distribution, -workerid) %>%
  group_by(distribution, item) %>%
  multi_boot_standard(col = "prop_choose")

ggplot(plot3,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("choose_l", "choose_m", "choose_r"),
                       labels = c("left", "middle", "right"))+
  facet_grid(~distribution, 
             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)"))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")
```

# Are participants choosing the middle item even when the middle item is wrong? 
```{r middle item, chose incorrectly}
plot4 <- data %>%
  filter(phase == 'test', correct_target1 == 0) %>%
  mutate(pick_l = ifelse(pickPos == "item_l", 1, 0), 
         pick_m = ifelse(pickPos == "item_m", 1, 0),
         pick_r = ifelse(pickPos == "item_r", 1, 0)) %>%
  group_by(distribution, workerid) %>%
  summarise(choose_l = mean(pick_l),
            choose_m = mean(pick_m),
            choose_r = mean(pick_r)) %>%
  gather(item, prop_choose, -distribution, -workerid) %>%
  group_by(distribution, item) %>%
  multi_boot_standard(col = "prop_choose")

ggplot(plot4,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("choose_l", "choose_m", "choose_r"),
                       labels = c("left", "middle", "right"))+
  facet_grid(~distribution, 
             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)"))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")
```

>>>>

---
title: "Discon Adult Analysis"
output: html_document
---

@@

```{r data preprocessing}
# Data pre-processing

@@

data <- raw_data %>%
  mutate(distribution = as.character(distribution),
         distribution = ifelse(distribution == "2:0", "c(2, 1, 0)", distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)", "c(3, 0, 0)", "c(1, 1, 1)", "c(2, 1, 0)")))
```
